Fractional Types

### 2019-11-23 fracGC/p.tex
One pass, maybe we should show some formalization of Pi in sec. 3. We have ⟦_⟧ for T, so at least we should also have ⟦_⟧ for U.

@@

\input{toffoli.tikz}

Note that in the construction of \AgdaFunction{TOFFOLIₙ} only wire manipulating operators
(multiplicative operators), ancilla allocation / de-allocation and \AgdaFunction{TOFFOLI}
are used.
\begin{figure}[ht]
  \PIFDtoffoli{}
\caption{\label{fig:toff}Generalized Toffoli Gates}
\end{figure}

@@

The constructor for machine states takes a number which is the size of
the memory list. This size is maintained throughout the execution,
even if the intermediate types change. As a small example, the
following is a trace of the execution of \AgdaFunction{CNOT} applied
to 𝕋, 𝕋:

@@

Note how the size of the list remains equal to 4 throughout the
execution, even if the individual elements change as types change and
the current index (i.e., the current value) changes.

@@

The main difference is that the state constructor does not take a
fixed size and indeed the size changes during execution as appropriate
to fit the elements of the type $A$. In particular, since fractional
values have a trivial representation, the cardinality of a fractional
type is 1, and hence $\eta$ used at type $A$ grows the size of the
memory list by an $|A|$-factor. As an illustrative example,
we show a trace of the execution of \AgdaFunction{id'}
from Sec.~\ref{sub:id} applied to 𝕋:

@@

The extraction map is fully implemented in the underlying Agda
formalization. We present the most significant highlights. There are
three important functions who signatures are below:

@@

The feedback loop in the diagram is realized using ancillae allocation
and de-allocation. The safety condition on de-allocation ensures that
the allocated value (now in the feedback loop) matches the
de-allocated value. Thus, the entire traced component is treated as an
ancilla value used internally used to perform the larger program but
leaving no memory footprint.

>>>>

%% Not sure about this
%% The formalization of $\Pi$ in Agda
%% \PI{}
%% And it is reversible:
%% \PIrev

@@

{\centering \input{toffoli.tikz}}

Note that in the construction of \AgdaFunction{TOFFOLIₙ} only wire manipulating operators
(multiplicative operators), ancilla allocation / de-allocation and \AgdaFunction{TOFFOLI}
are used.

\begin{figure}[ht]
  \PIFDtoffoli{}
\caption{\label{fig:toff}Generalized Toffoli Gates}
\end{figure}

@@

The constructor for machine states takes a number which is the size of
the memory. This size is maintained throughout the execution,
even if the intermediate types change. As a small example, the
following is a trace of the execution of \AgdaFunction{CNOT} applied
to 𝕋, 𝕋:

@@

Note how the size of the vector remains equal to 4 throughout the
execution, even if the individual elements change as types change and
the current index (i.e., the current value) changes.

@@

The main difference is that the state constructor does not take a
fixed size and indeed the size changes during execution as appropriate
to fit the elements of the type $A$. In particular, since fractional
values have a trivial representation, the cardinality of a fractional
type is 1, and hence $\eta$ used at type $A$ grows the size of the
memory by an $|A|$-factor. As an illustrative example,
we show a trace of the execution of \AgdaFunction{id'}
from Sec.~\ref{sub:id} applied to 𝕋:

@@

The extraction map is fully implemented in the underlying Agda
formalization. We present the most significant highlights. Here are
three important functions' signatures:

@@

The feedback loop in the diagram is realized using ancillae allocation
and de-allocation. The safety condition on de-allocation ensures that
the allocated value (now in the feedback loop) matches the
de-allocated value. Thus, the entire traced component is treated as an
ancilla value used internally to perform the larger program but
leaving no memory footprint.
